

\begin{rubric}{Academic Awards, and Miscellaneous Achievements}
% \subrubric{Scholarships and Grants}
% \entry*[2019--2020] Recipient,   Doctor   of  Philosophy   Scholarship,   University of Auckland.
% \entry*[2016--2019] Recipient,   Doctor   of  Philosophy   Scholarship   grant, Riddet Institute Centre of Research Excellence.
% \entry*[2011--2013] Recipient,  Masters  of technology  Scholarship  grant,  Ministry  of Human  Resource (MHRD) GATE scholarship.
% Entry* Recipient,  Riddet Travel  grant,   Riddet   Institute   Centre of Research Excellence (3,000 NZD).
\subrubric{Academic Awards}
%\entry*[2017] Recipient,  Riddet Travel  grant,   Riddet   Institute   Centre   of Research Excellence.
\entry*[2017] Recipient,  \textbf{Best Conference paper award}, 5th International Conference on Robotic Intelligence Technology and Applications (RiTA), Daejeon, Korea.
\entry*[2017] \textbf{Ranked 2nd}  in poster presentation in Delivery of Functionality in Complex Food Systems (DoF 2017) Conference.
\subrubric{Competitive Examinations}


%
\entry*[2011] \textbf{Percentile: 99.12\% (Rank 1,211/1,37,853)} in Graduate Aptitude Test of Engineering (GATE).
\entry*[2010] \textbf{Percentile: 96.00\%} in Graduate Aptitude Test of Engineering (GATE).
\entry*[2004] \textbf{Ranked 31st} in All India Junior mathematics Olympiad.
% 
\subrubric{Professional Activities}

\entry*[09/08/2025]{%
    Invited Speaker, \textbf{World Robotics Conference (WRC 2025)}, Beijing, China.  
    Presented research on \textit{Fabric modeling and perception for garment manufacturing}, exploring robotics and AI solutions for fabric representation, simulation, and real‑world applications.
  }
\entry*[03/08/2025]{
Workshop Organizing and Presentation
“Mesh-based Fabric State Estimation and Manipulation.”
IEEE International Conference on Mechatronics and Automation (ICMA 2025) – Workshop on Robotics for Automated Garment Production,
Beijing Empark Grand Hotel, Beijing, China.
}
%
\entry*[2021 - Current] Reviewer of IEEE Robotics and Automation Letters (RAL), IEEE International Conference on Robotics and Automation (ICRA), ASME Journal of Mechanisms and Robotics (JMR).
%
\entry*[2017 - Current] Member of the Institute of Electrical and Electronics Engineers (IEEE).
\entry*[2014] Former member of the Electrical Engineering Society (EES), IIT Roorkee, and NERIST Electronics Society (NES), NERIST.
\entry*[2006] Have an 'Outstanding  Certificate' in National Service Scheme (NSS) for contributing  in activities like blood donation camps, village cleanliness programmes and children education.
\end{rubric}