

\begin{rubric}{Employment History}


\entry*[2025 -- Current]%
	\textbf{Marie Skłodowska-Curie Postdoctoral Fellow } in the Dyson School of Engg, Imperial College London, Supervisor: Prof. Thrishantha Nanayakkara, 01/11/2025 -- Current.
    \par \textit{CASREx: Cable-driven Arm Soft Re-configurable Exoskeleton for Muscle Impairment Rehabilitation }
    
\entry*[2025]%
	\textbf{Senior Research Engineer--Control Systems } in the Center for Transformative Garment Production (TransGP), Supervisor: Prof. Kazuhiro Kosuge, 01/05/2025 -- 31/10/2025.
    \par \textit{ Physics-based Cloth Manipulation with policy generated from imitation learning.}
  
    \btit{Research Responsibilities:}
        \begin{itemize}
            \item Led a multidisciplinary team to develop high-performance models for fabric pre-sewing handling and folding. 
            \item Investigated feasibility and oversaw development and validation of robotic systems for fabric manipulation. 
            \item Translated industrial requirements into research deliverables through close collaboration and experimental analysis. 
            \item Contributed to scientific papers, technical reports, and grant proposals for dissemination and funding. 
            
            \btit{Other Responsibilities:}
            \begin{itemize}
                \item Mentoring and supervising PhD students, 3 at the moment.
                \item Reviewing, writing, and proofreading manuscripts.
            \end{itemize}
        \end{itemize}

\entry*[2024 -- 2025]%
	\textbf{Postdoctoral Fellow} in the Center for Transformative Garment Production (TransGP), Supervisor: Prof. Kazuhiro Kosuge, 02/07/2024 -- 30/04/2025.

\entry*[2024 -- 2025]%
	\textbf{Visiting Research Associate} in the Department of Electrical and Electronic Engineering, Hong Kong University (HKU), 02/07/2024 -- 31/10/2025.

\entry*[2021 -- 2024]%
	\textbf{Postdoctoral Fellow} in the Department of Mechanical and Automation, The Chinese University of Hong Kong. Supervisor: Prof. Darwin Lau, 01/03/2021 -- 30/06/2024
 \par \textit{Project title 1: Modeling and control of cable-driven robots with cable wrapping around obstacles and links.}
 \par \textit{Project title 2: Design of a cable-driven growing vine robot for safer false ceiling inspections.}

 Primary responsibilities:
 \begin{itemize}
     \item Conduct independent and collaborative research, contributing to larger projects under PI supervision.  
    \item Write research articles, proposals, and technical reports.  
    \item Mentor undergraduate and postgraduate students; delivered lectures for \btit{MAEG5090 Topics in Robotics}.
     %\item Writing and publishing high-quality journal articles \textbf{(5 published, 1 in review, and 2 in preparation)}.
 \end{itemize}
 
\entry*[2021 -- 2022]%
	\textbf{Visiting Postdoctoral Fellow} in Laboratoire des Sciences du Numérique de Nantes (LS2N), École Centrale de Nantes (ECN). Supervisors: Prof. Stephane Caro and Prof. Darwin Lau, 26/10/2021 -- 05/01/2022.
    \par \textit{Project title: Iterative-learning control of cable-driven parallel robot.}
\entry*[2017 -- 2020]%
	\textbf{Graduate Teaching Assistant} at The University of Auckland.
    \linebreak \textit{Courses taken: MECHENG 706: Mechatronics Design Projects, MECHENG 306: Design of Sensing and Actuating Systems, ENGGEN 115: Principles  of Engineering Design, ENGGEN  131: Introduction to Engineering Computation and Software Development.}
	\begin{itemize}
    \item Supervised undergraduate students on design projects, guiding problem‑solving and ensuring practical solutions.
    \item Delivered tutorials, workshops, and drop‑in clinics; provided support via online forums (Piazza, CANVAS).
    \item Managed laboratory sessions and coordinated TA activities, including safety briefings and student progress monitoring.
    % \item Marking reports and answer sheets to provide constructive feedback.
    % \item Preparation for tutoring and laboratory sessions.
    % \item Test invigilation.
    % \item Examining final reports for the completion of the design projects. 
    % \item Providing support to the students in debugging MATLAB, LabVIEW and C codes. 
    % \item Following courses have been taken during my tenure: 

    %     \hspace{1em}MECHENG 706: Mechatronics Design Projects. 
    %     % A range of projects that demonstrate the application and integration of engineering knowledge to create practical intelligent devices, machines and systems. 

    %     \hspace{1em}MECHENG 306: Design of Sensing and Actuating Systems.
    %     % A range of projects on mechatronic elements and systems, involving sensors, actuators and microcontrollers, as well as their interfacing. The design of mechatronic sub-systems, including interfacing, signal conditioning and processing, sensors, actuators, control technologies, software, systems modelling, simulation, analysis and design.

    %     \hspace{1em}ENGGEN 115: Principles  of Engineering Design. 
    %     % An introduction to the principles of design as a fundamental part of engineering practice and a foundation for subsequent design courses. Students are also introduced to essential drawing skills and CAD, and complete group-based design projects. Topics include systems life cycle, design, and introductions to professional issues such as health and safety, ethics, sustainability, cultural diversity, communication, leadership, and teamwork.

    %     \hspace{1em}ENGGEN  131: Introduction to Engineering Computation and Soft- 
        
    %     \hspace{6.5em} ware Development. 
    %     % \begin{table}[]
    %         % \begin{tabular}{lll}
    %         % a                    MECHENG & 706 & Mechatronics Design Projects.   \\
    %         % \multicolumn{1}{r}{} &   &    \\
    %         %                      &   &     \\
    %         %                      &   &   
    %         % \end{tabular}
    %         % % \end{table}
    %     % Introduction to problem solving in engineering through the use of the software package MATLAB, and the programming language C.
\end{itemize}

\entry*[2018 -- 2019]%
	\textbf{Research Assistant} at The University of Auckland, under the direction of Prof Peter Xu, 09/01/2018 -- 08/01/2019.
% \begin{itemize}
%     \item Measuring stent migration for esophageal stents of various design.
%     \item Developing different actuation protocols for soft-esophageal robot.
%     \item Writing reports containing the procedure and the results of the testing of the stents.
    
% \end{itemize}
% \entry*[06/01/2016--18/06/2016]%
% 	\textbf{ Assistant Professor} in Instrumentation and Control Engineering (ICE) at Galgotia's College of Engineering and Technology (GCET).
\entry*[2013--2016]%
	\textbf{ Lecturer (Assistant Professor Grade-1)} in School of Electrical, Electronics and Communication Engineering (SEECE) at Galgotia's University (GU), 19/07/2013--18/06/2016.
\begin{itemize}
    % \item Member of curriculum development team.
    \item Delivering lectures for undergraduate and postgraduate courses.
    \item Developing and constructing teaching materials for lectures.
    \item Supporting students in a pastoral/advisory role.
    \item Delivering laboratory sessions, and managing and supervising staffs and lab technicians.
    \item Supervision of final year undergraduate projects. 
\end{itemize}

\end{rubric}